---
title: "vGWAS plink tutorial"
author: "Kristian Ullrich"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: vGWAS.bib
vignette: >
  %\VignetteIndexEntry{vGWAS plink tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Vignette - vGWAS plink tutorial

### A Brief Tutorial of the R Package vGWAS using sparse genotype data

## Setup Notes

To use the vGWAS package, of course, an R environment is required. Visit:

http://www.r-project.org

and install R for the operating system.

Start R and in the R console, type the following command to install the package dependencies first:

```{r}
#install.packages("devtools")
#install.packages("hglm")
#install.packages("dglm")
#install.packages("doParallel")
#install.packages("foreach")
#install.packages("genio")
#install.packages("onewaytests")
#install.packages("Matrix")
#library(devtools)
#devtools::install_github("kullrich/vGWAS", build_vignettes = TRUE, dependencies = FALSE)
```

Now the package is installed in the R library.

## Example

It is assumed that genotype data is encoded as follows:

0: Homozygous ref allele
1: Heterozygous
2: Homozygous alt allele

Pre-processing can be done with e.g. 

## Remarks

The package source and further development information are on the R-Forge project page:
https://r-forge.r-project.org/projects/vgwas/

A reimplementation of `vGWAS` introducing the parallel function `vGWASparallel`
as a devtool package can be found here:
https://github.com/kullrich/vGWAS
